Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-05-29 paper/paper.Rmd
reply to Alex blockCV::buffering comments

(Subsection needs to be rewritten, see invisible comments. If this particular implementation is designed for binary classification problems, then a generic LOO with buffer is also needed, which should be introduced before this application-specific special case.)

@@

@@

The implementation also comes with support for *presence/background* data for binary responses.
In this scenario, only the presence values are considered validated. <!--- What is validated, in this context? Again, why overfit the code to such a very specific setting? -->
All other response observations are assumed to be absent without a proof for this assumption.
When setting argument `spDataType = "PB"`, the method only considers the *presence* observations in a CV scenario.
Background data is used for training the model by default unless argument `addBG = FALSE` is set for which only *presence* values not falling within the buffer zone of the respective fold are used for model training.

>>>>

<!--- (Subsection needs to be rewritten, see invisible comments. If this particular implementation is designed for binary classification problems, then a generic LOO with buffer is also needed, which should be introduced before this application-specific special case.) -->

<!--- P: By default the buffering implementation of blockCV behaves like a normal LOOCV.
It has additional features specific for SDM (presence-background data) but these are not active by default.
That is why I did not add `sperrorest::partition_loo()` because `blockCV::buffering()` does the same + has support for SDM. -->

@@

<!--- P: This addresses specifically the "buffering" function in the blockCV package which falls into the "buffering" category, the same applies to "spatial disc" from {sperrorest}.
Is this a potential misunderstanding with the overarching level 3 header "Buffering"? -->

@@

<!--- P: See my comment above, it might be that this is a misunderstanding. If not (or anyhow), we might want to clarify this more than to prevent such misunderstandings. -->

The implementation also comes with support for *presence/background* data for binary responses.
In this scenario, only the presence values are considered validated. <!--- What is validated, in this context? Again, why overfit the code to such a very specific setting? -->

<!--- P: Validated here means: the existence of the presence observations is validated, the background observations are artifical. This is a common procedure in SDM.
The blockCV buffering integration comes with support for presence/background handling which is important for SDM.
I think this should be explaind shortly then - which is what this section is about. -->

All other response observations are assumed to be absent without a proof for this assumption.
When setting argument `spDataType = "PB"`, the method only considers the *presence* observations in a CV scenario.
Background data is used for training the model by default unless argument `addBG = FALSE` is set for which only *presence* values not falling within the buffer zone of the respective fold are used for model training.
